A Study on Common Bug Fix Patterns in Rust

### 2022-10-11 sections/methodology.tex
merge is needed for methodology

We used the Pydriller library to mine software repositories. Pydriller provides APIs to extract commits from a Git repository and to search through different revisions of files. Algorithm~\ref{alg} shows how we used Pydriller to run the target repositories through our code analysis pipeline and populate two databases: one for borrow-checker related patterns (which involve items in \texttt{BCL}) and one for general patterns (which don't). For each repository, we search all commits that include bug-fixing related keywords within their commit messages. Here, we chose bug-fixing related keywords `bug', `error', `fault', `defect', and `fix'. 
% cite earlier work that does the search-for-keywords-to-identify-bugs; my earlier EMSE paper has that citation for instance. -- same issue as above, not sure how to cite

@@

Having collected our datapoints, our next task is to cluster them so that we can categorize bug patterns. Like~citehere, we use the DBSCAN clustering algorithm for two main reasons. Firstly, in contrast to k-means, it does not require the number of clusters in advance as an input to the algorithm. Secondly, it is a density-based clustering method, which means that it detects arbitrarily shaped clusters; centroid-based methods like k-means can't detect such clusters. We tried k-means and the more powerful fuzzy variant F-means and did not get useful clusters.

@@

% TODO fix this caption
\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{figs/clusters.png}
\caption{\label{fig:clustering} Clustering results with nine different combinations of parameters ($\epsilon=[10^{-2}, 10^{-3}, 10^{-4}], Z=[5,7,9])$}
\end{figure}

@@

That is why we carried out a manual analysis of clusters. In the manual analysis, we randomly pick 50 clusters; from each, cluster we randomly choose 10 datapoints. The person analyzing the cluster then looks at the code and specifies the clusters that contained more than five datapoints showing similar patterns. For the manual analysis, we used $\epsilon=0.0001, Z=5$ and $\epsilon=0.001, Z=5$, which were the best parameters for $D_g$ and $D_b$, resulting in 596 and 61 clusters, respectively. As a final step, we exclude clusters that contained datapoints from fewer than 3 projects. That is because we wanted our clusters to contain cross-project (e.g. potentially generalizable) patterns as much as possible.

@@

Similar to ..., following Cotroneo et al. definitions, we divide the clusters in three different groups:

>>>>

We used the Pydriller library to mine software repositories. Pydriller provides APIs to extract commits from a Git repository and to search through different revisions of files. Algorithm~\ref{alg} shows how we used Pydriller to run the target repositories through our code analysis pipeline and populate two databases: one for borrow-checker related patterns (which involve items in \texttt{BCL}) and one for general patterns (which don't). For each repository, we search all commits that include bug-fixing related keywords within their commit messages. Here, we chose bug-fixing related keywords based on the set introduced in \cite{zhang2018empirical}, excluding `nan' and `inf'.

@@

Having collected our datapoints, our next task is to cluster them so that we can categorize bug patterns. Like~\cite{hanam2016discovering}, we use the DBSCAN clustering algorithm for two main reasons. Firstly, in contrast to k-means, it does not require the number of clusters in advance as an input to the algorithm. Secondly, it is a density-based clustering method, which means that it detects arbitrarily shaped clusters; centroid-based methods like k-means can't detect such clusters. We tried k-means and the more powerful fuzzy variant Fuzzy C-means \cite{dunn1973fuzzy} and did not get useful clusters.

@@

% TODO fix this caption
\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{figs/clusters.pdf}
\caption{\label{fig:clustering} Clustering results with nine different combinations of parameters $\epsilon$ and $Z$, respectively separated in columns and rows. In each subplot, the two blue bars in the left indicate the number of clustered datapoints (the number is shown above each bar) after applying clustering on $D_g$ ($G_c$) and $D_b$ ($BC_{c}$), respectively. The two orange bars in the right show similar data but for noise datapoints. In each subplot's legend, $C_G$ and $C_B$ show the number of clusters obtained from $D_g$ and $D_b$, respectively}
\end{figure}

@@

That is why we carried out a manual analysis of clusters. In the manual analysis, we randomly pick 50 clusters; from each, cluster we randomly choose 10 datapoints. The person analyzing the cluster then looks at the code and specifies the clusters that contained more than five datapoints showing similar patterns. For the manual analysis, we used $\epsilon=0.0001, Z=5$ and $\epsilon=0.001, Z=5$, which were the best parameters for $D_g$ and $D_b$, resulting in 577 and 102 clusters, respectively. As a final step, we exclude clusters that contained datapoints from fewer than 3 projects. That is because we wanted our clusters to contain cross-project (e.g. potentially generalizable) patterns as much as possible.

@@

Similar to \cite{yang2022mining}, following Cotroneo et al. \cite{cotroneo2019analyzing} definitions, we divide the clusters in three different groups:
